Towards Automated Refactoring of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-07-01 sattose/paper.tex
Bit more about the research questions

\subsection{Research questions}
We have formalized the following research questions in order to improve upon the state-of-the-art in code duplication refactoring:

\textbf{RQ1.} How do we identify clones that we \textbf{can} refactor?\\
\textbf{RQ2.} How do we identify clones that we \textbf{should} refactor?\\
\textbf{RQ3.} To what extent can we \textbf{automate} the process of refactoring?

>>>>

\subsection{Research questions}
We have formalized the following research questions in order to improve upon the state-of-the-art in code duplication refactoring:\\
\textbf{RQ1.} How do we identify clones that we \textbf{can} refactor?\\
\textbf{RQ2.} How do we identify clones that we \textbf{should} refactor?\\
\textbf{RQ3.} To what extent can we \textbf{automate} the process of refactoring?\\

For \textbf{RQ1} we look into current clone definitions and clone detection methods. We then assess their suitability for refactoring purposes. For \textbf{RQ2} we look into to what extent clones can be filtered based on their impact on the system design when refactored. We do this by both determining good thresholds for the clone detection and by assessing the design implications of applying refactorings to the code. \textbf{RQ3} is currently still future work, hence the work in progress status of this paper.
